---
title: "Repurp: Drug–Gene Interaction Network Visualisation"
subtitle: "A Complete Workflow for Drug Repurposing Studies"
author: "Lucas VH Tran"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 9
    fig_height: 7
    css: bioc_style.css
    includes:
      in_header: header.html
vignette: >
  %\VignetteIndexEntry{Repurp: Drug--Gene Interaction Network Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  comment    = "#>",
  message    = FALSE,
  warning    = FALSE,
  fig.align  = "center",
  fig.width  = 9,
  fig.height = 7
)
# Suppress Windows font-metric warnings from base-R grid/igraph device
suppressWarnings(grDevices::pdf(NULL))
```

---

# Introduction

**Repurp** provides a unified, multi-backend workflow for building and
visualising drug–gene / biomarker interaction networks, with a focus on
atopic dermatitis (AD) drug repurposing. It ships seven complementary
visualisation backends, a curated AD drug reference table, and a built-in
colour system shared across all plot types.

**Visualisation backends:**

| # | Function(s) | Engine | Output | Best for |
|---|-------------|--------|--------|----------|
| 1 | `plot_dgi_igraph()` / `plot_dgi_igraph_core()` | igraph + qgraph | SVG + PNG | Fast bipartite, large networks |
| 2 | `plot_dgi_tripartite_igraph()` | igraph + qgraph | SVG + PNG | Gene × Drug × Pathway (base R) |
| 3 | `plot_dgi_ggraph()` / `plot_dgi_ggraph_core()` | ggraph + tidygraph | SVG + PNG | Tripartite, publication panels |
| 4 | `plot_dgi_ggraph_enhanced()` | ggraph + ggrepel + ggnewscale | SVG + PNG | Hub-labelled FR-layout, journals |
| 5 | `plot_dgi_ad_network()` | ggplot2 + ggrepel | SVG + PNG | Curated AD drug–biomarker network |
| 6 | `build_visnetwork()` / `build_visnetwork_tripartite()` | visNetwork | Interactive HTML | Exploratory, supplementary data |
| 7 | `plot_chord_dgi()` / `plot_chord_dgi_combined()` | circlize | SVG | Drug class overview, talks |
| 8 | `plot_dgi_heatmap()` | ggplot2 | SVG + PNG | Drug × Gene tile matrix |
| 9 | `plot_dgi_sankey()` | ggplot2 + ggalluvial | SVG + PNG | Drug class → Drug → Gene flow |
| 10 | `plot_dgi_dotmatrix()` | ggplot2 | SVG + PNG | Gene × Drug-class bubble matrix |

---

# Installation

```r
# Install from local source build
install.packages("path/to/Repurp", repos = NULL, type = "source")

# Core suggested packages (all visualisations)
install.packages(c(
  "ggplot2", "ggrepel", "ggnewscale",   # ggraph-family plots
  "ggraph", "tidygraph",                 # ggraph layouts
  "visNetwork",                          # interactive HTML
  "circlize",                            # chord diagrams
  "ggalluvial"                           # Sankey flow diagram
))
```

---

# Package data

```{r load-packages}
library(Repurp)
library(dplyr)
```

## Curated AD drugs

`repurp_ad_drugs()` returns a tibble of 18 established AD treatments with
drug class and molecular targets:

```{r ad-drugs}
repurp_ad_drugs()
```

## Curated MOA edges

`repurp_ad_edges()` returns 106 mechanism-of-action (MOA) edges linking each
AD drug to biomarker genes with edge type (`"direct"` or `"indirect"`):

```{r ad-edges}
repurp_ad_edges() |> dplyr::count(from, edge_type) |> head(12)
```

## Colour palettes

```{r palettes}
# Edge / interaction-type palette (14 types)
data.frame(type = names(dgi_edge_colors), hex = dgi_edge_colors)

# Node-type palette
dgi_node_colors

# Drug-class palette (13 classes)
data.frame(class = names(repurp_class_colors()), hex = repurp_class_colors())
```

---

# Synthetic demo dataset {#demo-data}

All examples below use a small in-memory dataset built from the curated AD
data, so you can run the vignette without a DGIdb download.

```{r build-synth}
# Compact synthetic DGI table (30 gene–drug edges)
synth_dgi <- tibble::tribble(
  ~Gene,     ~Drug,             ~InteractionType,
  "IL13",    "Dupilumab",       "INHIBITOR",
  "IL4R",    "Dupilumab",       "INHIBITOR",
  "IL13",    "Tralokinumab",    "INHIBITOR",
  "IL13",    "Lebrikizumab",    "INHIBITOR",
  "JAK1",    "Upadacitinib",    "INHIBITOR",
  "JAK1",    "Abrocitinib",     "INHIBITOR",
  "JAK1",    "Baricitinib",     "INHIBITOR",
  "JAK2",    "Baricitinib",     "INHIBITOR",
  "JAK2",    "Ruxolitinib",     "INHIBITOR",
  "JAK1",    "Ruxolitinib",     "INHIBITOR",
  "PDE4B",   "Crisaborole",     "INHIBITOR",
  "PDE4D",   "Crisaborole",     "INHIBITOR",
  "PDE4A",   "Roflumilast",     "INHIBITOR",
  "PDE4B",   "Roflumilast",     "INHIBITOR",
  "IL31RA",  "Nemolizumab",     "INHIBITOR",
  "AHR",     "Tapinarof",       "AGONIST",
  "NR3C1",   "Hydrocortisone",  "AGONIST",
  "NR3C1",   "Triamcinolone",   "AGONIST",
  "NR3C1",   "Betamethasone",   "AGONIST",
  "FKBP1A",  "Tacrolimus",      "BINDER",
  "FKBP1A",  "Pimecrolimus",    "BINDER",
  "PPP3CA",  "Tacrolimus",      "INHIBITOR",
  "PPP3CA",  "Cyclosporine",    "INHIBITOR",
  "DHFR",    "Methotrexate",    "INHIBITOR",
  "ATIC",    "Methotrexate",    "INHIBITOR",
  "IL18",    "Hydrocortisone",  "MODULATOR",
  "IL22",    "Triamcinolone",   "MODULATOR",
  "IL33",    "Betamethasone",   "MODULATOR",
  "STAT6",   "Upadacitinib",    "INHIBITOR",
  "TSLP",    "Dupilumab",       "MODULATOR"
)

# Verify the standardised structure
glimpse(synth_dgi)
```

## Preparing DGIdb data (your own files)

If you have downloaded interaction data from
[DGIdb v5](https://www.dgidb.org/), use `prepare_dgi_data()` to standardise
it:

```r
net_dat <- prepare_dgi_data(
  interactions = "interactions.tsv",   # path to DGIdb TSV download
  gene_list    = c("IL13", "IL4R", "JAK1", "JAK2", "PDE4B", "TSLP")
)
```

`prepare_dgi_data()` normalises column names, coerces `NA`/empty interaction
types to `"None"`, and filters to your gene list.

---

# Part 1: igraph / qgraph static networks

The igraph backend draws using base-R `plot.igraph()` with a
Fruchterman-Reingold layout computed by `qgraph`. Output is written to
SVG + PNG when `out_dir` is specified.

## Layout algorithm

The layout is computed by minimising the energy function:

$$
E(X) = \sum_{u < v} \left[
  k^2 \frac{1}{\|x_u - x_v\|} \;-\; \|x_u - x_v\|^2 \mathbf{1}_{\{u,v\}\in E}
\right]
$$

where $k = \sqrt{A / n}$ is the optimal pairwise distance ($A$ = canvas area,
$n$ = node count). Nodes repel uniformly but only connected pairs attract.

## 1a — Full bipartite network

```{r igraph-full, eval=requireNamespace("igraph", quietly=TRUE), fig.height=7}
plot_dgi_igraph(
  net_dat     = synth_dgi,
  title       = "AD Drug–Biomarker Network",
  gene_color  = "#009E73",
  drug_color  = "#F0E442",
  vertex_size = 7,
  label_cex   = 0.75
  # out_dir = "results/"  # uncomment to save SVG + PNG
)
```

Key parameters:

| Parameter | Default | Effect |
|-----------|---------|--------|
| `vertex_size` | `6` | Node circle radius |
| `label_cex` | `0.7` | Label scaling factor |
| `area_factor` | `2.0` | Canvas area multiplier — increase to spread nodes |
| `repulse_factor` | `1.0` | Node repulsion strength |
| `gene_color` | `"#009E73"` | Gene node fill |
| `drug_color` | `"#F0E442"` | Drug node fill |

## 1b — Core network (hub genes only)

`plot_dgi_igraph_core()` filters to genes with ≥ `min_gene_edges`
drug connections before plotting:

```{r igraph-core, eval=requireNamespace("igraph", quietly=TRUE), fig.height=6}
plot_dgi_igraph_core(
  net_dat        = synth_dgi,
  title          = "Core AD Network — genes ≥ 2 drugs",
  min_gene_edges = 2L
)
```

## 1c — Tripartite: Gene × Drug × Pathway

`plot_dgi_tripartite_igraph()` accepts a third node type — **Pathway** — via
`pathway_edges`. Without pathway edges it reduces to the bipartite case.

```r
# Build pathway_edges from STRING enrichment (see rbioapi)
library(rbioapi)
enrich <- rbioapi::rba_string_enrichment(ids = unique(synth_dgi$Gene), species = 9606)
pathway_edges <- dplyr::bind_rows(
  enrich[["KEGG"]] |> dplyr::mutate(category = "KEGG"),
  enrich[["Process"]] |> dplyr::mutate(category = "GO_Process")
) |>
  dplyr::filter(fdr < 0.05) |>
  tidyr::unnest(inputGenes) |>
  dplyr::select(from = inputGenes, to = description, edge_type = category)

dgi_e <- dplyr::select(synth_dgi, from = Gene, to = Drug, edge_type = InteractionType)

plot_dgi_tripartite_igraph(
  dgi_edges     = dgi_e,
  pathway_edges = pathway_edges,
  title         = "Tripartite: Gene × Drug × Pathway",
  out_dir       = "results/"
)
```

---

# Part 2: ggraph publication-quality networks

The ggraph backend returns a `ggplot` object — fully composable with
`patchwork`, `cowplot`, and standard ggplot2 theming.

```{r ggraph-setup, eval=requireNamespace("ggraph", quietly=TRUE)}
# Convert to the from/to/edge_type format expected by all ggraph functions
dgi_e <- dplyr::transmute(
  synth_dgi,
  from      = Gene,
  to        = Drug,
  edge_type = InteractionType
)
```

## 2a — Full tripartite view

```{r ggraph-full, eval=requireNamespace("ggraph", quietly=TRUE)}
p_full <- plot_dgi_ggraph(
  dgi_edges        = dgi_e,
  title            = "Drug–Gene Network (ggraph FR layout)",
  min_drug_targets = 1L,
  seed             = 42L
)
p_full
```

## 2b — Core view (Kamada-Kawai layout)

`plot_dgi_ggraph_core()` uses a Kamada-Kawai layout (default) and labels
every retained node:

```{r ggraph-core, eval=requireNamespace("ggraph", quietly=TRUE), fig.height=6}
p_core <- plot_dgi_ggraph_core(
  dgi_edges      = dgi_e,
  title          = "Core Drug–Gene Network (KK layout)",
  min_gene_edges = 2L,
  seed           = 42L
)
p_core
```

## 2c — Enhanced: FR layout + ggrepel + ggnewscale {.tabset}

`plot_dgi_ggraph_enhanced()` uses a `qgraph` FR layout with separate colour
scales for nodes and edges (via `ggnewscale`), and `ggrepel` for
non-overlapping labels. Two modes are available:

### Full mode

```{r ggraph-enh-full, eval=requireNamespace("ggrepel", quietly=TRUE)}
p_enh_full <- plot_dgi_ggraph_enhanced(
  dgi_edges        = dgi_e,
  mode             = "full",
  title            = "Enhanced DGI Network — full view",
  min_drug_targets = 2L,
  seed             = 42L
)
p_enh_full
```

### Core mode

```{r ggraph-enh-core, eval=requireNamespace("ggrepel", quietly=TRUE)}
p_enh_core <- plot_dgi_ggraph_enhanced(
  dgi_edges      = dgi_e,
  mode           = "core",
  title          = "Enhanced DGI Network — core view",
  min_gene_edges = 2L,
  seed           = 42L
)
p_enh_core
```

### Mode comparison

| Parameter | `"full"` | `"core"` |
|-----------|----------|----------|
| Gene filter | none | genes ≥ `min_gene_edges` drugs |
| Drug labels | hub drugs only (≥ `min_drug_targets`) | all drugs |
| Layout area | `2 × n²·⁰⁵` | same |
| `ggrepel` force | `0.5` | `1.0` |
| Use case | complete landscape | focused hub view |

---

## 2d — AD drug–biomarker network

`plot_dgi_ad_network()` draws the curated AD drugs with drug-class colour
coding and MOA edges:

```{r ad-network, eval=requireNamespace("ggrepel", quietly=TRUE), fig.height=8}
# Filter curated edges to genes present in our demo dataset
ad_e <- repurp_ad_edges() |>
  dplyr::filter(to %in% unique(synth_dgi$Gene))

p_adn <- plot_dgi_ad_network(
  edges     = ad_e,
  drug_info = repurp_ad_drugs(),
  title     = "AD Treatment Drug–Biomarker Network"
)
p_adn
```

Drug nodes are coloured by therapeutic category. Solid edges = direct
molecular target or DGIdb confirmed; dashed edges = pathway-level regulation.

---

# Part 3: Interactive visNetwork HTML widget

`build_visnetwork()` returns a `visNetwork` htmlwidget for in-document
rendering (RMarkdown / Quarto) or standalone HTML export.

## 3a — Bipartite widget

```{r visnet-bipartite, eval=requireNamespace("visNetwork", quietly=TRUE)}
vn_bip <- build_visnetwork(
  net_dat = synth_dgi,
  title   = "Interactive AD Drug–Biomarker Network"
)
vn_bip
```

## 3b — Tripartite widget

```r
# Requires pathway_edges data frame (see Part 1c for how to build it)
vn_tri <- build_visnetwork_tripartite(
  net_dat       = synth_dgi,
  pathway_edges = pathway_edges,
  title         = "Tripartite Interactive Network"
)
vn_tri
```

## 3c — Save to HTML

```r
save_visnetwork(vn_bip, "results/Fig_DGI_interactive.html", selfcontained = TRUE)
```

`selfcontained = TRUE` embeds all JavaScript and CSS in a single portable
`.html` file (recommended for supplementary data submissions).

---

# Part 4: Chord diagrams (circlize)

Chord diagrams show drug-class sectors on one arc and gene sectors on the
other, with link ribbons coloured by interaction type. The adjacency matrix
used for plotting is returned invisibly.

## 4a — Basic chord diagram

```{r chord-basic, eval=requireNamespace("circlize", quietly=TRUE), fig.height=8, fig.width=8}
# Build chord-ready edges from curated AD data
chord_e <- repurp_ad_edges() |>
  dplyr::filter(to %in% unique(synth_dgi$Gene)) |>
  dplyr::left_join(
    repurp_ad_drugs() |> dplyr::select(drug_name, class = category),
    by = c("from" = "drug_name")
  ) |>
  dplyr::rename(drug = from, gene = to) |>
  dplyr::mutate(int_type = "Curated MOA")

plot_chord_dgi(
  edges = chord_e,
  title = "AD Drugs × Biomarker Chord (curated)"
)
```

Key parameters:

| Parameter | Default | Effect |
|-----------|---------|--------|
| `transparency` | `0.15` | Link ribbon opacity (0 = opaque) |
| `min_drug_targets` | `1L` | Drop drugs with fewer gene targets |
| `gene_color` | `"#009E73"` | Gene sector colour |
| `svg_w`, `svg_h` | `32`, `32` | SVG output dimensions (inches) |

## 4b — Combined chord: curated AD + DGIdb hub drugs

`plot_chord_dgi_combined()` merges curated MOA edges with DGIdb hub drugs
(≥ `min_dgidb_targets` genes):

```r
# Build DGIdb hub edges (requires your own DGIdb data)
dgi_chord <- dplyr::transmute(synth_dgi,
  drug = Drug, gene = Gene, int_type = InteractionType
)

curated_chord <- repurp_ad_edges() |>
  dplyr::filter(to %in% unique(synth_dgi$Gene)) |>
  dplyr::left_join(
    repurp_ad_drugs() |> dplyr::select(drug_name, class = category),
    by = c("from" = "drug_name")
  ) |>
  dplyr::rename(drug = from, gene = to) |>
  dplyr::mutate(int_type = "Curated MOA")

plot_chord_dgi_combined(
  dgi_edges     = dgi_chord,
  curated_edges = curated_chord,
  title         = "AD + DGIdb Hub Drugs — Combined Chord",
  min_dgidb_targets = 2L,
  out_dir       = "results/"
)
```

---

# Part 5: Tile heatmap — Drug × Gene matrix {#heatmap}

`plot_dgi_heatmap()` renders a ggplot2 tile matrix where rows are drugs
sorted by drug class then degree, columns are genes sorted by degree, and
fill encodes the dominant interaction type for each drug–gene pair.

This plot is ideal for publications where a compact, annotation-rich overview
of the entire drug × gene space is needed.

```{r heatmap, eval=requireNamespace("ggplot2", quietly=TRUE), fig.height=7, fig.width=9}
p_heat <- plot_dgi_heatmap(
  dgi_edges  = dgi_e,
  drug_info  = repurp_ad_drugs(),
  title      = "Drug × Gene Interaction Heatmap",
  max_drugs  = 20L,
  max_genes  = 15L
)
p_heat
```

Key parameters:

| Parameter | Default | Effect |
|-----------|---------|--------|
| `max_drugs` | `60L` | Top-N drugs by degree to display |
| `max_genes` | `50L` | Top-N genes by degree to display |
| `drug_info` | `NULL` | Data frame with `drug_name` + `category` for row strips |
| `edge_palette` | `dgi_edge_colors` | Named hex vector for interaction types |

**Reading the heatmap:** Each cell represents a drug–gene pair with at least
one recorded interaction. The fill colour shows the most frequent interaction
type between that drug and gene. White cells indicate absence of interaction.
Rows are grouped by drug class, making it easy to spot within-class gene
targeting patterns.

---

# Part 6: Sankey / alluvial flow diagram {#sankey}

`plot_dgi_sankey()` renders a three-axis alluvial plot (requires `ggalluvial`):

$$
\text{Drug Class} \;\longrightarrow\; \text{Drug} \;\longrightarrow\; \text{Gene}
$$

Band width is proportional to the number of connections. Colour can encode
either drug class (`fill_by = "drug_class"`) or interaction type
(`fill_by = "edge_type"`).

## 6a — Colour by drug class

```{r sankey-class, eval=requireNamespace("ggalluvial", quietly=TRUE), fig.height=8, fig.width=10}
p_sank_cls <- plot_dgi_sankey(
  dgi_edges  = dgi_e,
  drug_info  = repurp_ad_drugs(),
  fill_by    = "drug_class",
  title      = "Drug Class → Drug → Gene Flow (by class)",
  max_genes  = 15L
)
p_sank_cls
```

## 6b — Colour by interaction type

```{r sankey-type, eval=requireNamespace("ggalluvial", quietly=TRUE), fig.height=8, fig.width=10}
p_sank_typ <- plot_dgi_sankey(
  dgi_edges  = dgi_e,
  drug_info  = repurp_ad_drugs(),
  fill_by    = "edge_type",
  title      = "Drug Class → Drug → Gene Flow (by interaction type)",
  max_genes  = 15L
)
p_sank_typ
```

Key parameters:

| Parameter | Default | Effect |
|-----------|---------|--------|
| `fill_by` | `"drug_class"` | Alluvia fill: `"drug_class"` or `"edge_type"` |
| `min_connections` | `1L` | Minimum edges per drug–gene pair to draw |
| `max_genes` | `30L` | Top-N genes to include |

**Reading the Sankey:** Follow a band from left to right to trace a drug
class's exposure through individual drugs into specific biomarker genes. Bands
that widen or narrow indicate unequal distribution of drug–gene connections
within a class. The `fill_by = "edge_type"` view reveals whether a drug class
predominantly inhibits, activates, or binds its targets.

---

# Part 7: Dot matrix — Gene × Drug-Class bubble chart {#dotmatrix}

`plot_dgi_dotmatrix()` produces a bubble/balloon plot where:

- **Y axis** = genes (sorted by total connections, most-connected at top)
- **X axis** = drug classes (sorted by total connections)
- **Dot size** = number of drug–gene connections within that class
- **Dot colour** = dominant interaction type
- **Label inside dot** = exact connection count

This is arguably the most information-dense single-panel summary for a drug
repurposing manuscript.

```{r dotmatrix, eval=requireNamespace("ggplot2", quietly=TRUE), fig.height=8, fig.width=9}
p_dot <- plot_dgi_dotmatrix(
  dgi_edges  = dgi_e,
  drug_info  = repurp_ad_drugs(),
  title      = "Gene × Drug-Class Connectivity Matrix",
  max_genes  = 15L
)
p_dot
```

Key parameters:

| Parameter | Default | Effect |
|-----------|---------|--------|
| `max_genes` | `40L` | Top-N genes by total degree |
| `min_connections` | `1L` | Minimum connections to draw a dot |
| `edge_palette` | `dgi_edge_colors` | Interaction-type colour mapping |

**Reading the dot matrix:** A large dot at position (gene, drug class)
indicates that multiple drugs in that class target this gene. The colour
reveals the mechanism: orange dots (ANTAGONIST), red (INHIBITOR), blue
(AGONIST), purple (BINDER). This view is particularly useful for identifying
genes that are targeted by multiple drug classes — strong candidates for
multi-mechanism repurposing strategies.

---

# Part 8: Multi-panel figures with patchwork

All ggraph/ggplot2 plot functions return a `ggplot` object, so they compose
directly with `patchwork`:

```r
library(patchwork)

# Build individual panels
p_enh <- plot_dgi_ggraph_enhanced(dgi_e, mode = "core", seed = 42L)
p_dot <- plot_dgi_dotmatrix(dgi_e, drug_info = repurp_ad_drugs())
p_ht  <- plot_dgi_heatmap(dgi_e, drug_info = repurp_ad_drugs())

# Two-column layout with shared title
(p_enh | p_dot) /
  p_ht +
  patchwork::plot_annotation(
    title    = "AD Drug–Biomarker Network Summary",
    subtitle = "Left: FR network (core). Right: dot matrix. Bottom: heatmap.",
    theme    = ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = "bold"))
  )
```

For igraph / circlize base-R plots in multi-panel layouts, use
`grDevices::recordPlot()` / `replayPlot()` or the `cowplot::draw_grob()`
approach:

```r
library(cowplot)
p_ig <- cowplot::as_grob(~plot_dgi_igraph(synth_dgi))
cowplot::plot_grid(p_ig, p_enh, ncol = 2, labels = c("A", "B"))
```

---

# Part 9: Comparing multiple gene sets

A common AD repurposing workflow runs the DGI pipeline separately for two
differential-expression contrasts and overlays the results:

```r
# Set 1: systemic AD vs healthy controls
dgi_sys  <- prepare_dgi_data("dgi_systemic.tsv",   gene_list = de_sys_genes)

# Set 2: non-systemic AD vs healthy controls
dgi_nsys <- prepare_dgi_data("dgi_nonsystemic.tsv", gene_list = de_nsys_genes)

# Convert both
e_sys  <- dplyr::transmute(dgi_sys,  from = Gene, to = Drug, edge_type = InteractionType)
e_nsys <- dplyr::transmute(dgi_nsys, from = Gene, to = Drug, edge_type = InteractionType)

# ggraph panels — returns ggplot, so patchwork works directly
p1 <- plot_dgi_ggraph_enhanced(e_sys,  mode = "core", title = "Systemic AD")
p2 <- plot_dgi_ggraph_enhanced(e_nsys, mode = "core", title = "Non-systemic AD")
p1 + p2

# Dot-matrix side-by-side
d1 <- plot_dgi_dotmatrix(e_sys,  drug_info = repurp_ad_drugs(), title = "Systemic AD")
d2 <- plot_dgi_dotmatrix(e_nsys, drug_info = repurp_ad_drugs(), title = "Non-systemic AD")
d1 + d2
```

Genes present in both sets can be highlighted by adding a shared-gene column
to the node aesthetics before plotting.

---

# Colour reference

## Interaction types (`dgi_edge_colors`)

```{r edge-pal, fig.height=3, fig.width=7, eval=requireNamespace("ggplot2", quietly=TRUE)}
ec <- data.frame(
  type  = names(dgi_edge_colors),
  hex   = unname(dgi_edge_colors),
  stringsAsFactors = FALSE
)
ec$type <- factor(ec$type, levels = rev(ec$type))

ggplot2::ggplot(ec, ggplot2::aes(x = 1, y = type, fill = hex)) +
  ggplot2::geom_tile(color = "white", width = 0.9, height = 0.85) +
  ggplot2::geom_text(ggplot2::aes(label = paste0(type, "  ", hex)),
                     x = 1, size = 3.2, hjust = 0.5, color = "grey10") +
  ggplot2::scale_fill_identity() +
  ggplot2::theme_void() +
  ggplot2::labs(title = "dgi_edge_colors — interaction type palette") +
  ggplot2::theme(
    plot.title = ggplot2::element_text(size = 11, face = "bold", hjust = 0.5)
  )
```

## Drug classes (`repurp_class_colors()`)

```{r class-pal, fig.height=3.5, fig.width=7, eval=requireNamespace("ggplot2", quietly=TRUE)}
rc <- data.frame(
  class = names(repurp_class_colors()),
  hex   = unname(repurp_class_colors()),
  stringsAsFactors = FALSE
)
rc$class <- factor(rc$class, levels = rev(rc$class))

ggplot2::ggplot(rc, ggplot2::aes(x = 1, y = class, fill = hex)) +
  ggplot2::geom_tile(color = "white", width = 0.9, height = 0.85) +
  ggplot2::geom_text(ggplot2::aes(label = paste0(class, "  ", hex)),
                     x = 1, size = 3.0, hjust = 0.5, color = "grey10") +
  ggplot2::scale_fill_identity() +
  ggplot2::theme_void() +
  ggplot2::labs(title = "repurp_class_colors() — drug class palette") +
  ggplot2::theme(
    plot.title = ggplot2::element_text(size = 11, face = "bold", hjust = 0.5)
  )
```

## Node types (`dgi_node_colors`)

```{r node-pal}
data.frame(
  node_type = names(dgi_node_colors),
  hex       = unname(dgi_node_colors)
)
```

---

# Summary

```{r summary-table, echo=FALSE}
tbl <- data.frame(
  `Function` = c(
    "prepare_dgi_data()",
    "plot_dgi_igraph()",
    "plot_dgi_igraph_core()",
    "plot_dgi_tripartite_igraph()",
    "plot_dgi_ggraph()",
    "plot_dgi_ggraph_core()",
    "plot_dgi_ggraph_enhanced()",
    "plot_dgi_ad_network()",
    "build_visnetwork()",
    "build_visnetwork_tripartite()",
    "save_visnetwork()",
    "plot_chord_dgi()",
    "plot_chord_dgi_combined()",
    "plot_dgi_heatmap()",
    "plot_dgi_sankey()",
    "plot_dgi_dotmatrix()"
  ),
  `Engine` = c(
    "dplyr / stringr",
    "igraph + qgraph",
    "igraph + qgraph",
    "igraph + qgraph",
    "ggraph + tidygraph",
    "ggraph + tidygraph",
    "ggraph + ggrepel + ggnewscale",
    "ggplot2 + ggrepel + ggnewscale",
    "visNetwork",
    "visNetwork",
    "visNetwork",
    "circlize",
    "circlize",
    "ggplot2",
    "ggplot2 + ggalluvial",
    "ggplot2"
  ),
  `Output` = c(
    "tibble",
    "SVG + PNG",
    "SVG + PNG",
    "SVG + PNG",
    "ggplot",
    "ggplot",
    "ggplot",
    "ggplot",
    "htmlwidget",
    "htmlwidget",
    "HTML file path",
    "SVG",
    "SVG",
    "ggplot",
    "ggplot",
    "ggplot"
  ),
  `New in v0.2` = c(
    "", "", "", "", "", "", "", "", "", "", "", "", "",
    "✓", "✓", "✓"
  ),
  check.names = FALSE
)
knitr::kable(tbl, caption = "All Repurp exported functions — v0.2.0.")
```

---

# Session information

```{r session}
sessionInfo()
```
